Do larger watersheds respond different to forest cover change? Re-analysing a global data set.

### 2022-01-01 paper/Forest_and_Water/Forest_and_Water.Rmd
final changes old laptop

---
title: Do larger watersheds respond different to forest cover change? Re-analysing a global data set.
author:
  - name: R. Willem Vervoort
    email: willem.vervoort@sydney.edu.au
    affiliation: The University of Sydney, INIA
    footnote: 1
  - name: Eliana Nervi
    email: eliananervi@gmail.com
    affiliation: INIA
    footnote: 2
  - name: Jimena Alonso
    email: jalonso@fing.edu.uy
    affiliation: IMFIA
    footnote: 2
address:
  - code: The University of Sydney
    address: School of Life and Environmental Sciences, The University of Sydney, Sydney, NSW 2006, Australia
  - code: INIA
    address: Instituto Nacional de Investigación Agropecuaria, INIA-Uruguay, Ruta 48 km 10, Rincon del Colorado, 90100 Canelones, Uruguay
  - code: IMFIA
    address: Institute of Fluid Mechanics and Environmental Engineering, School of Engineering, Universidad de la República, 11200 Montevideo, Uruguay
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
abstract: |
  This is the abstract.
  It consists of two paragraphs.
journal: "Journal of Hydrology"
date: "`r Sys.Date()`"
bibliography: forest_and_water.bib
linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
editor_options: 
  chunk_output_type: console
---

@@

```{r, echo = F, warning = F, message=F, eval =F}
png("DataExploration.png", width = 2500, height = 1800, res = 300)
All_data %>%
  pivot_longer(c(DeltaF_perc, DeltaQf_perc, Area_km2, Pa_mm, E0), 
               names_to = "variable", values_to = "value") %>%
  ggplot(aes(value)) + geom_histogram(fill = "steelblue", bins=50) + theme_bw() +
  facet_wrap(~variable, scales = "free", labeller = labeller(variable = 
    c("Area_km2" = "Area (km2)",
      "DeltaF_perc" = "Delta Forest (%)",
      "DeltaQf_perc" = "Delta Flow (%)",
      "E0" = "Annual Potential E (mm)",
      "Pa_mm" = "Annual Rainfall (mm)"))) +   
  theme(axis.title = element_text(size = rel(2)),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 45, hjust = 1))
dev.off()
```

@@

```{r, echo = F, warning = F, message=F, eval =F}
# plot to show the difference
png("Increase_decrease.png", width = 2500, height = 1800, res = 300)
All_data2 %>%
  ggplot(aes(DeltaF_perc_pos,DeltaQf_perc, colour = Forest_Sign)) + 
  geom_point() +  
  facet_wrap(~Forest_Sign, ncol=1, scales = "free") + 
  theme_bw() + scale_colour_manual(name = "direction of forest change", values = c("increase" = "blue", "decrease" = "red")) +
  xlab("Change in forest cover %") + ylab("Change in flow %")
dev.off()

@@

```{r, echo = F}
pander(Zhang_all2 %>% filter(Dryness > 4) %>% select(Latitude, Longitude,`Watershed name`), caption = "Watersheds for which the dryness inddex > 4")
```

@@

model6_all <- gam(DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + 
                    s(log10(Area_km2), bs="ts") + s(Dryness, bs="ts" ) + 
                     s(length, bs="ts") +
                    Precip_data_type +  Assessment_technique + Forest_type +
                    Hydrological_regime
                    , data = All_data2)
#summary(model6_all)
#gam.check(model6_all)
#plot(model6_all)
pander(round(summary(model6_all)$p.table,2))
pander(round(summary(model6_all)$s.table,2))
plot(model6_all, select = 3)
```

@@

```{r, eval =T, echo =F}
All_data2 %>%
  ggplot(aes(Assessment_technique, log10(Area_km2))) + 
  geom_boxplot(colour = "blue") + theme_bw()
```

@@

<!--reduce drynes < 4 -->
```{r model7_noLatb}
model7_noLatb <- gam(DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + 
                    s(Dryness, bs="ts" ) + #s(Latitude, bs="ts") + 
                      s(log10(Area_km2), bs="ts") + s(length,bs="ts") +
                    Precip_data_type +  Assessment_technique + Forest_type +
                    Hydrological_regime, data = All_data2 %>% filter(length< 60))
summary(model7_noLatb)
plot(model7_noLatb)
```

```{r, echo = F}
png("flow_forest_byArea.png", width = 2500, height = 1800, res = 300)
All_data2 %>%
  ggplot(aes(DeltaF_perc_pos, DeltaQf_perc, colour = Assessment_technique,size = log10(Area_km2), 
             shape = Forest_Sign)) + geom_point(alpha = 0.5) +
  theme_bw() + ylab("% change in flow") +
  theme(axis.title = element_text(size = rel(2)),
        axis.text = element_text(size = rel(1.5))) +
  xlab("% change in forestry") + #scale_y_log10() +
  scale_size_continuous(name = "log10(Area in km2)") +
  scale_colour_discrete(name = "Assessment Technique") +
  scale_shape_discrete(name = "Forest cover direction")
dev.off()
```

@@

There are further confouding factors in the data, which were also classified by @filoso2017 and these create biases in the data set that can impact the overall assessment. For example, snow dominated hydrological regimes (SD), which are weakly significant, are dominated by Coniferous Forests (CF), while the majority of the rain dominated regimes are all broadleaf forests (BF). However, the forest type classification is very coarse and does not fully capture possible physiological differences that could affect evapotranspiration and therefore changes in streamflow.

>>>>

---
title: Do larger watersheds respond different to forest cover change? Re-analysing a global data set.
author:
  - name: R. Willem Vervoort
    email: willem.vervoort@sydney.edu.au
    affiliation: DARE, The University of Sydney
    footnote: 1
  - name: Eliana Nervi
    email: eliananervi@gmail.com
    affiliation: INIA
    footnote: 2
  - name: Jimena Alonso
    email: jalonso@fing.edu.uy
    affiliation: IMFIA
    footnote: 2
address:
  - code: DARE
    address: ARC Training Centre Data Analytics for Resources and the Environment
  - code: The University of Sydney
    address: School of Life and Environmental Sciences, The University of Sydney, Sydney, NSW 2006, Australia
  - code: INIA
    address: Project Manager, FPTA 357 Instituto Nacional de Investigación Agropecuaria, INIA-Uruguay, Ruta 48 km 10, Rincon del Colorado, 90100 Canelones, Uruguay
  - code: IMFIA
    address: Institute of Fluid Mechanics and Environmental Engineering, School of Engineering, Universidad de la República, 11200 Montevideo, Uruguay
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
abstract: |
  This is the abstract.
  It consists of two paragraphs.
journal: "Journal of Hydrology"
date: "`r Sys.Date()`"
bibliography: forest_and_water.bib
linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
editor_options: 
  chunk_output_type: console
---

@@

```{r, echo = F, warning = F, message=F, eval =F}
png("DataExploration.png", width = 2500, height = 1800, res = 300)
All_data %>%
  pivot_longer(c(DeltaF_perc, DeltaQf_perc, Area_km2, Pa_mm, E0), 
               names_to = "variable", values_to = "value") %>%
  ggplot(aes(value)) + geom_histogram(fill = "steelblue", bins=50) + theme_bw() +
  facet_wrap(~variable, scales = "free", labeller = labeller(variable = 
    c("Area_km2" = "Area (km2)",
      "DeltaF_perc" = "Delta Forest (%)",
      "DeltaQf_perc" = "Delta Flow (%)",
      "E0" = "Annual Potential E (mm)",
      "Pa_mm" = "Annual Rainfall (mm)"))) +   
  theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.2)),
        strip.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 45, hjust = 1))
dev.off()
```

@@

```{r, echo = F, warning = F, message=F, eval =F}
# plot to show the difference
png("Increase_decrease.png", width = 2500, height = 1800, res = 300)
All_data2 %>%
  ggplot(aes(DeltaF_perc_pos,DeltaQf_perc, colour = Forest_Sign)) + 
  geom_point() +  
  facet_wrap(~Forest_Sign, ncol=1, scales = "free") + 
  theme_bw() + 
    theme(axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.2)),
        legend.text = element_text(size = rel(1.2)),
        legend.title = element_text(size = rel(1.2)),
        strip.text = element_text(size = rel(1.5))) + 
  scale_colour_manual(name = "Forest change direction", 
                      values = c("increase" = "blue", "decrease" = "red")) +
  xlab("Change in forest cover %") + ylab("Change in flow %")
dev.off()

@@

```{r, echo = F}
pander(Zhang_all2 %>% filter(Dryness > 4) %>% select(Latitude, Longitude,`Watershed name`), caption = "Watersheds for which the dryness index > 4")
```

@@

model6_all <- gam(DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + 
                    s(log10(Area_km2), bs="ts") + s(Dryness, bs="ts" ) + 
                     s(length, bs="ts") +
                    Precip_data_type +  Assessment_technique + Forest_type +
                    Hydrological_regime
                    , data = All_data2)
#summary(model6_all)
#gam.check(model6_all)
#plot(model6_all)
pander(round(summary(model6_all)$p.table,2))
pander(round(summary(model6_all)$s.table,2))
plot(model6_all, select = 2)
```

@@

```{r, eval =F, echo =F}
png("AssessmentTechnique_byArea.png", width = 2500, height = 1800, res = 300)
All_data2 %>%
  ggplot(aes(Assessment_technique, log10(Area_km2))) + 
  geom_boxplot(colour = "blue") + theme_bw() +
    theme(axis.title = element_text(size = rel(2)),
        axis.text = element_text(size = rel(1.5)))
dev.off()
```

```{r assessment, fig.cap="Boxplot of the log base 10 of the watershed area (in km2) for the different assessment techniques, showing the dominance of small watersheds in the paired watershed experiments", out.width="90%", echo=F}

include_graphics("AssessmentTechnique_byArea.png")
```

@@

\newpage

<!--reduce drynes < 4 -->
```{r model7_noLatb, echo = F}
model7_noLatb <- gam(DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + 
                    s(Dryness, bs="ts" ) + #s(Latitude, bs="ts") + 
                      s(log10(Area_km2), bs="ts") + s(length,bs="ts") +
                    Precip_data_type +  Assessment_technique + Forest_type +
                    Hydrological_regime, data = All_data2 %>% filter(length< 60))
#summary(model7_noLatb)
#plot(model7_noLatb)
pander(round(summary(model7_noLatb)$p.table,2))
pander(round(summary(model7_noLatb)$s.table,2))
plot(model7_noLatb)
summary(model7_noLatb)
```

### remove the assessment techniques with very small numbers

```{r model8_reduc_assess, echo = F}
All_data3 <- All_data2 %>%
  filter(Assessment_technique != "EA, HM" & Assessment_technique != "PWE, HM" & Assessment_technique != "QPW, EA" )

model8_assess <- gam(DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + 
                    s(Dryness, bs="ts" ) + #s(Latitude, bs="ts") + 
                      s(log10(Area_km2), bs="ts") + s(length,bs="ts") +
                    Precip_data_type +  Assessment_technique + Forest_type +
                    Hydrological_regime, data = All_data3 %>% filter(length< 60))
#summary(model7_noLatb)
#plot(model7_noLatb)
pander(round(summary(model8_assess)$p.table,2))
pander(round(summary(model8_assess)$s.table,2))
plot(model8_assess)
summary(model8_assess)

```{r, echo = F}
png("flow_forest_byArea.png", width = 2500, height = 1800, res = 300)
All_data2 %>%
  ggplot(aes(DeltaF_perc_pos, DeltaQf_perc, colour = Assessment_technique,size = log10(Area_km2), 
             shape = Forest_Sign)) + geom_point(alpha = 0.5) +
  theme_bw() + ylab("% change in flow") +
  theme(axis.title = element_text(size = rel(2)),
        axis.text = element_text(size = rel(1.5))) +
  xlab("% change in forest cover") + #scale_y_log10() +
  scale_size_continuous(name = "log10(Area in km2)") +
  scale_colour_discrete(name = "Assessment Technique") +
  scale_shape_discrete(name = "Forest cover direction")
dev.off()
```

@@

There are further confounding factors in the data, which were also classified by @filoso2017 and these create biases in the data set that can impact the overall assessment. For example, snow dominated hydrological regimes (SD), which are weakly significant, are dominated by Coniferous Forests (CF), while the majority of the rain dominated regimes are all broadleaf forests (BF). However, the forest type classification is very coarse and does not fully capture possible physiological differences that could affect evapotranspiration and therefore changes in streamflow.

### 2022-01-01 paper/Forest_and_Water/Forest_and_Water.tex
final changes old laptop

  \title{Do larger watersheds respond different to forest cover change?
Re-analysing a global data set.}
    \author[The University of Sydney, INIA]{R. Willem Vervoort\corref{1}}
   \ead{willem.vervoort@sydney.edu.au} 
    \author[INIA]{Eliana Nervi\corref{2}}
   \ead{eliananervi@gmail.com} 
    \author[IMFIA]{Jimena Alonso\corref{2}}
   \ead{jalonso@fing.edu.uy} 
      \address[The University of Sydney]{School of Life and Environmental Sciences, The University of Sydney,
Sydney, NSW 2006, Australia}
    \address[INIA]{Instituto Nacional de Investigación Agropecuaria, INIA-Uruguay, Ruta 48
km 10, Rincon del Colorado, 90100 Canelones, Uruguay}
    \address[IMFIA]{Institute of Fluid Mechanics and Environmental Engineering, School of
Engineering, Universidad de la República, 11200 Montevideo, Uruguay}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

Quitting from lines 461-462 (Forest\_and\_Water.Rmd) Error in filter(.,
Dryness \textgreater{} 4) : object `Zhang\_all2' not found Calls:
\ldots{} withVisible -\textgreater{} eval -\textgreater{} eval
-\textgreater{} pander -\textgreater{} \%\textgreater\% -\textgreater{}
select -\textgreater{} filter In addition: Warning messages: 1: In
eval(expr, envir, enclos) : NAs introduced by coercion 2: In eval(expr,
envir, enclos) : NAs introduced by coercion

@@

\includegraphics{Forest_and_Water_files/figure-latex/unnamed-chunk-22-1.pdf}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{model7_noLatb <-}\StringTok{ }\KeywordTok{gam}\NormalTok{(DeltaQf_perc }\OperatorTok{~}\StringTok{ }\NormalTok{DeltaF_perc_pos }\OperatorTok{+}\StringTok{ }\NormalTok{Forest_Sign }\OperatorTok{+}\StringTok{ }
\StringTok{                    }\KeywordTok{s}\NormalTok{(Dryness, }\DataTypeTok{bs=}\StringTok{"ts"}\NormalTok{ ) }\OperatorTok{+}\StringTok{ }\CommentTok{#s(Latitude, bs="ts") + }
\StringTok{                      }\KeywordTok{s}\NormalTok{(}\KeywordTok{log10}\NormalTok{(Area_km2), }\DataTypeTok{bs=}\StringTok{"ts"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{s}\NormalTok{(length,}\DataTypeTok{bs=}\StringTok{"ts"}\NormalTok{) }\OperatorTok{+}
\StringTok{                    }\NormalTok{Precip_data_type }\OperatorTok{+}\StringTok{  }\NormalTok{Assessment_technique }\OperatorTok{+}\StringTok{ }\NormalTok{Forest_type }\OperatorTok{+}
\StringTok{                    }\NormalTok{Hydrological_regime, }\DataTypeTok{data =}\NormalTok{ All_data2 }\OperatorTok{%>%}\StringTok{ }\KeywordTok{filter}\NormalTok{(length}\OperatorTok{<}\StringTok{ }\DecValTok{60}\NormalTok{))}
\KeywordTok{summary}\NormalTok{(model7_noLatb)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Family: gaussian 
## Link function: identity 
## 
## Formula:
## DeltaQf_perc ~ DeltaF_perc_pos + Forest_Sign + s(Dryness, bs = "ts") + 
##     s(log10(Area_km2), bs = "ts") + s(length, bs = "ts") + Precip_data_type + 
##     Assessment_technique + Forest_type + Hydrological_regime
## 
## Parametric coefficients:
##                             Estimate Std. Error t value Pr(>|t|)    
## (Intercept)                 -12.5901    18.2493  -0.690 0.490850    
## DeltaF_perc_pos               0.2764     0.1021   2.708 0.007197 ** 
## Forest_Signincrease         -23.5034     6.9108  -3.401 0.000772 ***
## Precip_data_typeOB          -11.8739    14.1588  -0.839 0.402419    
## Precip_data_typeSG           16.9396    16.3313   1.037 0.300543    
## Assessment_techniqueEA, HM   -8.2703     3.5091  -2.357 0.019143 *  
## Assessment_techniqueHM       28.0181    12.3042   2.277 0.023557 *  
## Assessment_techniquePWE      39.2429    12.0840   3.247 0.001310 ** 
## Assessment_techniquePWE, HM -14.4779     5.5623  -2.603 0.009753 ** 
## Assessment_techniqueQPW      33.8032    20.7827   1.627 0.105002    
## Assessment_techniqueQPW, EA  35.5789    25.2225   1.411 0.159506    
## Assessment_techniqueSH       42.8100    12.7078   3.369 0.000864 ***
## Forest_typeCF                -3.8554     8.1687  -0.472 0.637324    
## Forest_typeMF                -4.0151     8.6538  -0.464 0.643047    
## Hydrological_regimeSD         6.4841    10.0569   0.645 0.519641    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Approximate significance of smooth terms:
##                          edf Ref.df     F p-value  
## s(Dryness)         3.586e+00      9 1.665  0.0132 *
## s(log10(Area_km2)) 7.053e-01      9 0.293  0.0510 .
## s(length)          2.302e-10      9 0.000  0.9953  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Rank: 39/42
## R-sq.(adj) =  0.273   Deviance explained = 31.4%
## GCV = 2119.6  Scale est. = 1992.7    n = 289
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot}\NormalTok{(model7_noLatb)}
\end{Highlighting}
\end{Shaded}

@@

@@

There are further confouding factors in the data, which were also
classified by Filoso et al. (2017) and these create biases in the data
set that can impact the overall assessment. For example, snow dominated
hydrological regimes (SD), which are weakly significant, are dominated
by Coniferous Forests (CF), while the majority of the rain dominated
regimes are all broadleaf forests (BF). However, the forest type
classification is very coarse and does not fully capture possible
physiological differences that could affect evapotranspiration and
therefore changes in streamflow.

>>>>

  \title{Do larger watersheds respond different to forest cover change?
Re-analysing a global data set.}
    \author[DARE, The University of Sydney]{R. Willem Vervoort\corref{1}}
   \ead{willem.vervoort@sydney.edu.au} 
    \author[INIA]{Eliana Nervi\corref{2}}
   \ead{eliananervi@gmail.com} 
    \author[IMFIA]{Jimena Alonso\corref{2}}
   \ead{jalonso@fing.edu.uy} 
      \address[DARE]{ARC Training Centre Data Analytics for Resources and the Environment}
    \address[The University of Sydney]{School of Life and Environmental Sciences, The University of Sydney,
Sydney, NSW 2006, Australia}
    \address[INIA]{Project Manager, FPTA 357 Instituto Nacional de Investigación
Agropecuaria, INIA-Uruguay, Ruta 48 km 10, Rincon del Colorado, 90100
Canelones, Uruguay}
    \address[IMFIA]{Institute of Fluid Mechanics and Environmental Engineering, School of
Engineering, Universidad de la República, 11200 Montevideo, Uruguay}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

Quitting from lines 471-472 (Forest\_and\_Water.Rmd) Error in filter(.,
Dryness \textgreater{} 4) : object `Zhang\_all2' not found Calls:
\ldots{} withVisible -\textgreater{} eval -\textgreater{} eval
-\textgreater{} pander -\textgreater{} \%\textgreater\% -\textgreater{}
select -\textgreater{} filter In addition: Warning messages: 1: In
eval(expr, envir, enclos) : NAs introduced by coercion 2: In eval(expr,
envir, enclos) : NAs introduced by coercion

@@

\begin{figure}
\includegraphics[width=0.9\linewidth]{AssessmentTechnique_byArea} \caption{Boxplot of the log base 10 of the watershed area (in km2) for the different assessment techniques, showing the dominance of small watersheds in the paired watershed experiments}\label{fig:assessment}
\end{figure}

@@

\newpage
-12.59\strut
18.25\strut
-0.69\strut
0.49\strut
0.28\strut
2.71\strut
0.01\strut
-23.5\strut
6.91\strut
-3.4\strut
-11.87\strut
14.16\strut
-0.84\strut
0.4\strut
16.94\strut
16.33\strut
1.04\strut
-8.27\strut
3.51\strut
-2.36\strut
28.02\strut
12.3\strut
2.28\strut
39.24\strut
12.08\strut
3.25\strut
-14.48\strut
5.56\strut
-2.6\strut
0.01\strut
33.8\strut
20.78\strut
1.63\strut
0.11\strut
35.58\strut
25.22\strut
1.41\strut
0.16\strut
42.81\strut
12.71\strut
3.37\strut
-3.86\strut
8.17\strut
-0.47\strut
0.64\strut
-4.02\strut
8.65\strut
-0.46\strut
0.64\strut
6.48\strut
10.06\strut
0.64\strut
0.52\strut

\begin{longtable}[]{@{}ccccc@{}}
\toprule
\begin{minipage}[b]{0.30\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
edf\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
Ref.df\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
F\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
p-value\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{s(Dryness)}\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
3.59\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
9\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
1.67\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
0.01\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{s(log10(Area\_km2))}\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.71\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
9\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.29\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
0.05\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{s(length)}\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
9\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
1\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\hypertarget{remove-the-assessment-techniques-with-very-small-numbers}{%
\subsubsection{remove the assessment techniques with very small
numbers}\label{remove-the-assessment-techniques-with-very-small-numbers}}
\begin{minipage}[b]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\centering
\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-18.71\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
19.02\strut
-0.98\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.33\strut
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.29\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
2.83\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-23.26\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
7.15\strut
-3.25\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-11.25\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
14.19\strut
-0.79\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.43\strut
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
18.43\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
16.43\strut
1.12\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.26\strut
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
32.02\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
12.76\strut
2.51\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.01\strut
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
44.48\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
12.97\strut
3.43\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
38.12\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
21.21\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
46.79\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
13.17\strut
3.55\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-3.3\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
8.23\strut
-0.4\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.69\strut
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
-3.88\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
8.69\strut
-0.45\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.66\strut
\begin{minipage}[t]{0.34\columnwidth}\centering
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
5.73\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\centering
10.11\strut
0.57\strut
\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
0.57\strut

\begin{longtable}[]{@{}ccccc@{}}
\toprule
\begin{minipage}[b]{0.30\columnwidth}\centering
~\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
edf\strut
\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
Ref.df\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
F\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\centering
p-value\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{s(Dryness)}\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
3.51\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
9\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
1.96\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{s(log10(Area\_km2))}\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.7\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
9\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.24\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
0.08\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\centering
\textbf{s(length)}\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
9\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\centering
0.99\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\includegraphics{Forest_and_Water_files/figure-latex/model8_reduc_assess-1.pdf}
\includegraphics{Forest_and_Water_files/figure-latex/model8_reduc_assess-2.pdf}
\includegraphics{Forest_and_Water_files/figure-latex/model8_reduc_assess-3.pdf}

@@

There are further confounding factors in the data, which were also
classified by Filoso et al. (2017) and these create biases in the data
set that can impact the overall assessment. For example, snow dominated
hydrological regimes (SD), which are weakly significant, are dominated
by Coniferous Forests (CF), while the majority of the rain dominated
regimes are all broadleaf forests (BF). However, the forest type
classification is very coarse and does not fully capture possible
physiological differences that could affect evapotranspiration and
therefore changes in streamflow.
